New Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimisation Choices

### 2024-09-23 jso.qmd
inequality signs

\begin{proof}
Let $r_1 := \underset{r}{\arg \min }\,g_1'(r)$ and $r_2 := \underset{r}{\arg \min }\,g_2'(r)$.
Since $g_1$ is convex, $g_1''(r) >= 0 \; \forall r \in [0, D]$, meaning that $g_1'$ is an increasing function, taking its minimum for $r_1=0$. As a result, $\varsigma(g_1)=-4 \times g'(0) \times 0 =0$.
Since $g_2$ is concave, $g_2''(r) <= 0 \; \forall r \in [0, D]$, meaning that $g_2'$ is a decreasing function, taking its minimum for $r_2=D>0$. Since $g_2$ is strictly decreasing, $g_2'(r) < 0 \; \forall r \in [0, D]$. In particular $g_2'(D)<0$. As a result $\varsigma(g_2)=-4 \times g'(D) \times D >0$. This proves that $\varsigma(g_1) < \varsigma(g_2)$.
\end{proof}

>>>>

\begin{proof}
Let $r_1 := \underset{r}{\arg \min }\,g_1'(r)$ and $r_2 := \underset{r}{\arg \min }\,g_2'(r)$.
Since $g_1$ is convex, $g_1''(r) \geq 0 \; \forall r \in [0, D]$, meaning that $g_1'$ is an increasing function, taking its minimum for $r_1=0$. As a result, $\varsigma(g_1)=-4 \times g'(0) \times 0 =0$.
Since $g_2$ is concave, $g_2''(r) \leq 0 \; \forall r \in [0, D]$, meaning that $g_2'$ is a decreasing function, taking its minimum for $r_2=D>0$. Since $g_2$ is strictly decreasing, $g_2'(r) < 0 \; \forall r \in [0, D]$. In particular $g_2'(D)<0$. As a result $\varsigma(g_2)=-4 \times g'(D) \times D >0$. This proves that $\varsigma(g_1) < \varsigma(g_2)$.
\end{proof}
